SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/problems.tex
remove labels on unapproached problems

\begin{problem}\label{prob:infgivecode}
How can suitable inference engines be made available to all users?
\end{problem}

@@

\begin{problem}\label{prob:sayanything}
With a centralised ontology approach, how can we ensure that anybody is enabled to say
anything?
\end{problem}

@@

\begin{problem}\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
\end{problem}

>>>>

\begin{problem}%\label{prob:infgivecode}
How can suitable inference engines be made available to all users?
\end{problem}

@@

\begin{problem}%\label{prob:sayanything}
With a centralised ontology approach, how can we ensure that anybody is enabled to say
anything?
\end{problem}

@@

\begin{problem}%\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
\end{problem}
